MSDS 7333 Case Study 06

### 2017-06-19 MSDS7333_CaseStudy06_MBaldree_BBrock_TElkins_AKelly.Rmd
pushing updates

```{r}
df = subset(offline, posX == 24 & posY == 4 & !(mac %in% remainingAP), c(signal, angle, mac))
plotDensitySignalStrength(df)
```
<font color = "red"> <b> &uarr; having issues with this diplaying properly... &uarr;</b> </font>

@@

```{r}
offline$posXY = paste(offline$posX, offline$posY, sep="-")

# create data frames for each combination
byLocAngleAP = with(offline, by(offline, list(posXY, angle, mac), function(x) x))
```

Now, we calculate the summary statistics:
```{r}
signalSummary = lapply(byLocAngleAP, function(oneLoc) {
  ans = oneLoc[1, ]
  ans$medSignal = median(oneLoc$signal)
  ans$avgSignal = mean(oneLoc$signal)
  ans$num = length(oneLoc$signal)
  ans$sdSignal = sd(oneLoc$signal)
  ans$iqrSignal = IQR(oneLoc$signal)
  ans
})
offlineSummary = do.call("rbind", signalSummary)
```

The Standard Deviation of the average signal strength per targeted AP

@@

@@

```{r}
macs = unique(offlineSummary$mac)
online = readData("online.final.trace.txt", subMacs = macs)
online$posXY = paste(online$posX, online$posY, sep = "-")
length(unique(online$posXY))
tabonlineXYA = table(online$posXY, online$angle)
#output shows measurements were taken at all angles throughout the floor
tabonlineXYA
```

>>>>

```{r, fig.height=10}
df = subset(offline, posX == 24 & posY == 4 & !(mac %in% remainingAP), c(signal, angle, mac))
plotDensitySignalStrength(df)
```

@@

```{r}
offlineSummary = createOfflineSummary(offline)
```

### <font color = "red"> &darr; this section may no longer be needed. Now missing from the original code. &darr;</font>  
```{r}
#offline$posXY = paste(offline$posX, offline$posY, sep="-")
#
# create data frames for each combination
#byLocAngleAP = with(offline, by(offline, list(posXY, angle, mac), function(x) x))
```

Now, we calculate the summary statistics:
```{r}
#signalSummary = lapply(byLocAngleAP, function(oneLoc) {
#  ans = oneLoc[1, ]
#  ans$medSignal = median(oneLoc$signal)
#  ans$avgSignal = mean(oneLoc$signal)
#  ans$num = length(oneLoc$signal)
#  ans$sdSignal = sd(oneLoc$signal)
#  ans$iqrSignal = IQR(oneLoc$signal)
#  ans
#})
#offlineSummary = do.call("rbind", signalSummary)
```
### <font color = "red"> &uarr; this section may no longer be needed. Now missing from the original code. &uarr;</font>

The Standard Deviation of the average signal strength per targeted AP:

@@

From this figure, it is apparent that there is considerable overlap between the two distributions of signal strength. This is evidence in favor of keeping both addresses in the analysis to provide greater coverage.

@@

```{r}
macs = unique(offlineSummary$mac)
macs
online = readData("online.final.trace.txt", subMacs = macs)
online$posXY = paste(online$posX, online$posY, sep = "-")
length(unique(online$posXY))
tabonlineXYA = table(online$posXY, online$angle)
#output shows measurements were taken at all angles throughout the floor
tabonlineXYA
```
